A Derivative Tracking Model for Wind Power Forecast Error

### 2020-07-13 LaTeX_Code/Paper/Supplementary Material/supp_mat_1.tex
Updated supplementary material

%% Packages
\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage[authoryear]{natbib}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%\RequirePackage{graphicx}% uncomment this for including figures

@@

>>>>

%% Packages
\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage[authoryear]{natbib}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{float}
\usepackage{commath}
\usepackage{fancybox}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{url}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%\RequirePackage{graphicx}% uncomment this for including figures

@@

\section{Seasonality effect}

To guaranty an homogeneous year, we study the Mean Absolute Error (MAE) for each provider and for each day. In Figures (\ref{MAE_pA}), (\ref{MAE_pB}), and (\ref{MAE_pC}), we can see the daily and weekly MAE for the providers A, B, and C, respectively.\\
To compute the vector that we are piloting, we realize the operation
\begin{equation*}
\hat{V}(j) =\frac{1}{145} \sum_{i=1}^{145}|V(i,j)|\quad\text{where}\quad j\in\{1,\dots,147\}.
\end{equation*}
Recall that $V(i,j)$ is the normalized error between the ADME real production and the UTE forecast at time $i$ and for the day $j$.

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_A/MAE.eps}
\caption{Daily and weekly for the provider A.}
\label{MAE_pA}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_B/MAE.eps}
\caption{Daily and weekly for the provider B.}
\label{MAE_pB}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_C/MAE.eps}
\caption{Daily and weekly for the provider C.}
\label{MAE_pC}
\end{figure}

\section{Hourly effect}

We want to see the error throughout the day. We compute the MAE for each provider for each measurement during the day. In Figures (\ref{HMAE_pA}), (\ref{HMAE_pB}), and (\ref{HMAE_pC}), we can see the hourly MAE for the providers A, B, and C, respectively.\\

To compute the vector that we are piloting, we realize the operation
\begin{equation*}
\hat{V}(i) =\frac{1}{147} \sum_{j=1}^{147}|V(i,j)|\quad\text{where}\quad i\in\{1,\dots,145\}.
\end{equation*}
Recall that $V(i,j)$ is the normalized error between the ADME real production and the UTE forecast at time $i$ and for the day $j$.\\

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_A/H_MAE.eps}
\caption{MAE along the day for the provider A.}
\label{HMAE_pA}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_B/H_MAE.eps}
\caption{MAE along the day for the provider B.}
\label{HMAE_pB}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_C/H_MAE.eps}
\caption{MAE along the day for the provider C.}
\label{HMAE_pC}
\end{figure}

\section{Forecast Error Vs Forecast:}

We plot the forecast error as a function of the forecast value for each provider. In Figures (\ref{sA}), (\ref{sB}), and (\ref{sC}), we can see this plots for the providers A, B, and C, respectively.

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/scatter/prov_A/scatter.eps}
\caption{MAE along the day for the provider A.}
\label{sA}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/scatter/prov_B/scatter.eps}
\caption{MAE along the day for the provider B.}
\label{sB}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/scatter/prov_C/scatter.eps}
\caption{MAE along the day for the provider C.}
\label{sC}
\end{figure}

### 2020-07-13 LaTeX_Code/Paper/aoas-template.tex
Updated supplementary material

\begin{figure}[ht!]
\centering
\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Optimal.eps}
\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
\caption{Density histograms for error transitions. Using provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE. On the left, simulations use $(\theta_0^V,\alpha^V)$. On the right, simulations use $(\theta_0^Z,\alpha^Z)$.}
\label{fig:hists}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{plots/delta/contour_delta.eps}
\caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}
\label{fig:delta}
\end{figure}

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Optimal.pdf}\quad
\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Lamperti_Optimal.pdf}
\caption{Density histograms for error transitions. Using provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE. On the left, simulations use $(\theta_0^V,\alpha^V)$. On the right, simulations use $(\theta_0^Z,\alpha^Z)$.}
\label{fig:hists}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{plots/delta/contour_delta.png}
\caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}
\label{fig:delta}
\end{figure}
